Models pretest

### 2022-12-07 Submission/Models_pretest.Rmd
president fixed effect, and changes to model names

# model
model_logit_con <- glm(con_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, family=binomial(link = "logit"),
                       data = ama_model)
model_logit_ei <- glm(EI_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + party, family=binomial(link = "logit"),
                      data = ama_model)
model_logit_sd <- glm(SD_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + party,
                      family=binomial(link = "logit"), data = ama_model)
model_logit_sov <- glm(sov_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party,
                       family=binomial(link = "logit"), data = ama_model)
model_logit_all <- glm(amazon_speech ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party,
                       family=binomial(link = "logit"), data = ama_model2)

stargazer::stargazer(model_logit_con, model_logit_ei, model_logit_sd,
                     model_logit_sov, model_logit_all, digits = 6,
                     no.space = TRUE, title = "Logistic Regressions")
```

@@

# model fe
model_logit_con_fe <- plm(con_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, data = ama_model,
                         model = "within", index = "year")
model_logit_ei_fe <- plm(EI_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, data = ama_model,
                         model = "within", index = "year")
model_logit_sd_fe <- plm(SD_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, data = ama_model,
                         model = "within", index = "year")
model_logit_sov_fe <- plm(sov_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, data = ama_model,
                         model = "within", index = "year")
model_logit_all_fe <- plm(amazon_speech ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, data = ama_model2,
                         model = "within", index = "year")

stargazer::stargazer(model_logit_con_fe, model_logit_ei_fe, model_logit_sd_fe,
                     model_logit_sov_fe, model_logit_all_fe, digits = 6,
                     no.space = TRUE, title = "Fixed-effects Regressions")
```

@@

# model
model_logit_con_lag <- glm(con_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, family=binomial(link = "logit"),
                       data = ama_model_lag)
model_logit_ei_lag <- glm(EI_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + party, family=binomial(link = "logit"),
                      data = ama_model_lag)
model_logit_sd_lag <- glm(SD_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + party,
                      family=binomial(link = "logit"), data = ama_model_lag)
model_logit_sov_lag <- glm(sov_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party,
                       family=binomial(link = "logit"), data = ama_model_lag)
model_logit_all_lag <- glm(amazon_speech ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party,
                       family=binomial(link = "logit"), data = ama_model2_lag)

stargazer::stargazer(model_logit_con_lag, model_logit_ei_lag, model_logit_sd_lag,
                     model_logit_sov_lag, model_logit_all_lag, digits = 6,
                     no.space = TRUE, title = "Logistic Regressions with Lagged Year")
```

@@

>>>>

# model
a1 <- glm(con_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, family=binomial(link = "logit"),
                       data = ama_model)
a2 <- glm(EI_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + party, family=binomial(link = "logit"),
                      data = ama_model)
a3 <- glm(SD_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + party,
                      family=binomial(link = "logit"), data = ama_model)
a4 <- glm(sov_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party,
                       family=binomial(link = "logit"), data = ama_model)
a5 <- glm(amazon_speech ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party,
                       family=binomial(link = "logit"), data = ama_model2)

stargazer::stargazer(a1, a2, a3,
                     a4, a5, digits = 6,
                     no.space = TRUE, title = "Logistic Regressions")
```

@@

# model fe
b1 <- plm(con_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, data = ama_model,
                         model = "within", index = "year")
b2 <- plm(EI_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, data = ama_model,
                         model = "within", index = "year")
b3 <- plm(SD_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, data = ama_model,
                         model = "within", index = "year")
b4 <- plm(sov_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, data = ama_model,
                         model = "within", index = "year")
b5 <- plm(amazon_speech ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, data = ama_model2,
                         model = "within", index = "year")

stargazer::stargazer(b1, b2, b3,
                     b4, b5, digits = 6,
                     no.space = TRUE, title = "Fixed-effects Regressions")
```

@@

# model
c1 <- glm(con_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, family=binomial(link = "logit"),
                       data = ama_model_lag)
c2 <- glm(EI_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + party, family=binomial(link = "logit"),
                      data = ama_model_lag)
c3 <- glm(SD_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + party,
                      family=binomial(link = "logit"), data = ama_model_lag)
c4 <- glm(sov_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party,
                       family=binomial(link = "logit"), data = ama_model_lag)
c5 <- glm(amazon_speech ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party,
                       family=binomial(link = "logit"), data = ama_model2_lag)

stargazer::stargazer(c1, c2, c3,
                     c4, c5, digits = 6,
                     no.space = TRUE, title = "Logistic Regressions with Lagged Year")
```

@@

```{r models lagged ideology, fig.cap="Logistic Regressions Output Lagged Deforestation with Ideology", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}

#table(ama_model$president, ama_model$party)

ideology_vdem <- readRDS("~/Documents/GitHub/amazondef/Submission/V-Dem-CPD-Party-V2.rds") %>% 
dplyr::filter(country_name == "Brazil") %>%
dplyr::select(v2pashname, v2xpa_antiplural, v2xpa_popul, v2pariglef) %>%
tidyr::drop_na() %>%
dplyr::rename(party = v2pashname) %>%
group_by(party) %>%
summarise(anti_pluralism = mean(v2xpa_antiplural),
populism = mean(v2xpa_popul),
left_right = mean(v2pariglef))

ama_model_lag <- dplyr::left_join(ama_model_lag, ideology_vdem)

ama_model2_lag <- dplyr::left_join(ama_model2_lag, ideology_vdem)

# model
c1 <- glm(con_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + populism + anti_pluralism + left_right, family=binomial(link = "logit"),
                       data = ama_model_lag)
c2 <- glm(EI_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + populism + anti_pluralism + left_right, family=binomial(link = "logit"),
                      data = ama_model_lag)
c3 <- glm(SD_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + populism + anti_pluralism + left_right,
                      family=binomial(link = "logit"), data = ama_model_lag)
c4 <- glm(sov_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + populism + anti_pluralism + left_right,
                       family=binomial(link = "logit"), data = ama_model_lag)
c5 <- glm(amazon_speech ~ as.factor(location_cat) + election_year +
                         def_year + AAI + populism + anti_pluralism + left_right,
                       family=binomial(link = "logit"), data = ama_model2_lag)

stargazer::stargazer(c1, c2, c3,
                     c4, c5, digits = 6,
                     no.space = TRUE,
                     title = "Logistic Regressions with Lagged Year and Party Ideology")
```

```{r models president fixed effect, fig.cap="Logistic Regressions Output with President fixed effecr", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}

d1 <- plm(con_vs_all ~ as.factor(location_cat) + 
                         def_year + AAI + election_year, data = ama_model_lag,
                         model = "within", index = "president")
d2 <- plm(EI_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year, data = ama_model_lag,
                         model = "within", index = "president")
d3 <- plm(SD_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year, data = ama_model_lag,
                         model = "within", index = "president")
d4 <- plm(sov_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year, data = ama_model_lag,
                         model = "within", index = "president")
d5 <- plm(amazon_speech ~ as.factor(location_cat) +
                         def_year + AAI + election_year, data = ama_model2_lag,
                         model = "within", index = "president")

stargazer::stargazer(d1, d2, d3,
                     d4, d5, digits = 6,
                     no.space = TRUE,
                     title = "Logistic Regressions with president fixed-effects")
